Irt plot extra

### 2022-02-22 appendix-1.Rmd
Landscape figures (TIC and IIC)

```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30,41) had relatively flat information curves', out.width='100%', out.height='100%'}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```

>>>>

```{r IF, fig.env = "sidewaysfigure", echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30, 41) had relatively flat information curves', out.width="100%", out.height="120%", out.extra = ""}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```

### 2022-02-22 manuscript.Rmd
Landscape figures (TIC and IIC)

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---

@@

as_tibble(desc_table) -> desc_tibble 
as_kable_extra(desc_table, format = "latex",booktabs = T) %>% 
  kable(col.names=c("Variable", "Overall, n=690$^{1}$","EFA Sample, n=428$^{1}$", "CFA sample, n=262$^{1}$", "p", "q$^{2}$"), escape = FALSE)-> desc_kable #save it as a knitr::kable

@@

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%', out.width=}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

```{r Testinfo, fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime. Along x-axis we plotted the underlying latent trait continumm for each factor. Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE}

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header.tex
header-includes:
  - \usepackage{rotating}
  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---

@@

as_tibble(desc_table) -> desc_tibble 
as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable

@@

```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime. Along x-axis we plotted the underlying latent trait continumm for each factor. Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}
